### 2022-09-27 main/chapter_context.tex
add glashow-salam-weinberg citations
add bjorken november citation

Mathematically, the Standard Model is described by a quantized gauge field
theory with the symmetry group
$SU\!(3)_C \!\times\! SU\!(2)_L \!\times\! U\!(1)_Y$,
meaning that its Lagrangian is invariant under local operations of group
elements on its fields in certain representations.

@@

The fermions of the Standard Model are listed in Table~\TODO{}.
% Glashow-Salam-Weinberg
Older Standard Models included only two fermion generations and no
neutrino masses~\cite{
wells2020discovery
},\TODO{cite more}
but a modern model must include both three generations and non-zero neutrino
masses to be compatible with experiment:
three fermion generations are directly established
\TODO{kaon mixing CPV~\cite{
cronin1964evidence,
kabayasji1973cpv
}, direct observation of tau/top/bottom~\cite{
perl1977evidence,
herb1977observation,
abachi1995observation
}, Z width~\cite{
lep2006precision
}
},
as are neutrino masses from their flavour oscillations demonstrating that
they experience proper time~\cite{
kamiokande1998measurement,
superk1998evidence,
superk1999measurement,
lsnd1998evidence
}.

>>>>

Mathematically, the Standard Model is described by a quantized gauge field
theory with the symmetry group
$SU\!(3)_C \times SU\!(2)_L \times U\!(1)_Y$,
meaning that its Lagrangian is invariant under local operations of group
elements on its fields in certain representations.

@@

\TODO{
Glashow-Salam-Weinberg~\cite{
glashow1959renorm,
weinberg1967model,
salam1959weak
}
}

\TODO{charm november revolution~\cite{bjorken1985november}}

The fermions of the Standard Model are listed in Table~\TODO{}.
Older Standard Models included only two fermion generations and no
neutrino masses~\cite{
wells2020discovery
},\TODO{cite more}
but a modern model must include both three generations and non-zero neutrino
masses to be compatible with experiment:
three fermion generations are directly established
\TODO{kaon mixing CPV~\cite{
cronin1964evidence,
kabayasji1973cpv
}, direct observation of tau/top/bottom~\cite{
perl1977evidence,
herb1977observation,
abachi1995observation
}, Z width~\cite{
lep2006precision
}
},
as are neutrino masses from their flavour oscillations demonstrating that
they experience proper time~\cite{
kamiokande1998measurement,
superk1998evidence,
superk1999measurement,
lsnd1998evidence
}.
